\documentclass[a4paper,11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}

\title{vector dependent magnetism near domain wall}
\author{Ben Rosemeyer}

\begin{document}

\maketitle
\tableofcontents

\begin{abstract}
\end{abstract}

\section{Derivation of equation}
\section{characteristic wave vectors for position from wall}
\section{steapness of domain wall}
\section{andreev coherence in SNS structures}
various quantities oscillate with length of N/S regions
\section{tight binding susceptibility near interface?}
"Direct imaging..." paper reports "The magnitude and temperature dependence of the paramagnetic response indicate that the vast majority of the electrons at the interface are localized and do not contribute to trasport measurements"
\section{Zeeman Field?}
Anomalous Meissner effect in NS junction with spin-active interface
Yokoyama, tanaka
Usadel equations at interface with small applied field. Results in possible divergent susceptibility which also can oscillate with temperature and/or length of normal/sc part
\section{self consistent delta near interface}
Usadel
\section{superconductor ferromagnet interfaces}
Competition between superconductivity and magnetism in ferromagnet/superconductor heterostructures, Izyumov, Proshin, Khusainov
FFLO type state, but layered, not one material.
layered structures display various magnetic order between FM layers (magnetisation only in FM part)
magnetic order and sc order can have 0-phase or $\pi$-phase difference between adjacent layers
\section{anomalous meisner effect in pnictide superconductors}
Prozorov et al
susceptibility becomes constant with increasing field for field cooled samples.
interesting magnetisation curves
\section{direct imaging of the coexistence of ferromagnetism and supeconductivity at the $LaAlO_3$/$SrTiO_3$ interface}
Bert, Kalisky et al
Temperature dependence of susceptibility.
both are non-magnetic and insulating.
Interface has 2D mobile electrons with sc.
M-I and I-SC transitions with applied electric field



\end{document}
